--- 
title: "Activity 1"
author: "Mahdis Moghadasi"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---
# Main Research Interest

  My main research interests are landuse changes and environmental planning, accessibility, Transportation planning and Machine Learning.
  
  During my Master education, my supervisor and I have published two articles on how land use changes during 1996-2016 in one of Iran's metropolitan areas and I also researched about the potential accessibility of the transportation network in Iran in my master's thesis. Since I was faced with a large amount of data so I decided to learn machine learning and data analysis.
 
  In addition, I will also be researching mobility justice in my PhD, which is of great interest to me both in terms of data analysis and in terms of subject matter. Because I think the achievements of this study will have a tremendous impact on the lives of citizens and It will also have great scientific achievements for me as a PhD student.

# Favorites
## *Favorite Music*
1. [The Last Time](https://music.apple.com/us/album/the-last-time-feat-gary-lightbody/1440935340?i=1440935568)
   + Taylor Swift
   
2. [Million Reasons](https://music.apple.com/us/album/million-reasons/1440893782?i=1440893897)
   + Lady Gaga
   
3. [Bored](https://music.apple.com/us/album/bored/1440880821?i=1440881181)
   + Billie Eilish
   
4. [Memories](https://music.apple.com/us/album/memories/1479600900?i=1479600902)
   + Maroon 5
   
5. [Little do you know](https://music.apple.com/us/album/little-do-you-know/895611637?i=895611647)
   + Alex & Sierra
   
## *Favorite Equation*
$(x^3+4*x^2)/sqrt(x+3)$

## *Favorite Artists*
Name  | Achievement
------------- | -------------
Taylor Swift  | Taylor is the first female solo act to win the Grammy for “Album of the Year” twice
Lady Gaga  | In 2020, Lady Gaga became the first person to be honored with the MTV Tricon award. This award was created to celebrate "highly accomplished artists across three disciplines."
shakira  | Rock singer Shakira is ten-time Grammy Award winner.
Adele  | English singer-songwriter Adele has received various awards and nominations. She is the recipient of nine Brit Awards, an Academy Award, a Golden Globe Award, fifteen Grammy Awards, eighteen Billboard Music Awards, five American Music Awards, and two Ivor Novello Awards for Songwriter of the Year.
Celine Dion  | Dion has won over 100 awards, including the Lifetime Achievement Icon Award, The Canadian Arts & Fashion International Style Icon Award, 5 Grammys and was appointed one of France’s “Chevalier de la Légion d’Honneur” for her merits and contributions to France.

# A chunk of code
**Part 1**
```{r, echo=TRUE}
data(cars)
str(cars)
summary(cars)
plot(cars)
```

**Part2**

```{r, echo=FALSE}
hist(cars$speed)
boxplot(cars$dist)
```

**Part3**

The mean speed of cars was `r mean(cars$speed)` .



